---
title: "mia-rfid"
output:
  html_document: default
  pdf_document: default
---

loading in packages
```{r, warning=FALSE, message=FALSE, results='hide'}
library(tidyverse)
library(data.table)
```

loading in data
```{r, warning=FALSE, message=FALSE, results='hide'}
df1 <- read_csv2("raw_data/Tracking/rawdata20210604.csv")
df2 <- read_csv2("raw_data/Tracking/rawdata20210605.csv")
df3 <- read_csv2("raw_data/Tracking/rawdata20210606.csv")
df4 <- read_csv2("raw_data/Tracking/rawdata20210607.csv")
df5 <- read_csv2("raw_data/Tracking/rawdata20210608.csv")
df6 <- read_csv2("raw_data/Tracking/rawdata20210609.csv")
df7 <- read_csv2("raw_data/Tracking/rawdata20210610.csv")
```

stacking the data together
```{r, warning=FALSE, message=FALSE, results='hide'}
df <- rbind(df1, df2, df3, df4, df5, df6, df7)

df$data <- as.character(df$data)

df
```

creating milliseconds (ms) column
```{r, warning=FALSE, message=FALSE, results='hide'}
df$date <- format(as.POSIXct(df$datetimestamp,format="%d.%m.%Y %H:%M:%S:%OS"),"%m.%d.%Y")
  
df$time <- sub("^\\S+\\s+", '', df$datetimestamp)

xx <- strsplit(df$time, split=":")

#xx
xxx <- matrix(unlist(xx), ncol = 4, byrow = TRUE)
#xxx[,1]
#xxx[,2]
#xxx[,3]
#as.numeric(xxx[,4])

df$ms<-
  (3600000 * as.numeric(xxx[,1])) +
(60000 * as.numeric(xxx[,2])) +
(1000 * as.numeric(xxx[,3])) +
(1 * as.numeric(xxx[,4]))
```


editing ms column to account for number days past
```{r, warning=FALSE, message=FALSE, results='hide'}
day_1 <- df %>% filter(date == "06.04.2021")

  day_1$ms <- as.numeric(unlist(day_1$ms)) - 40089792

day_2 <- df %>% filter(date == "06.05.2021")

  day_2$ms <- (as.numeric(unlist(day_2$ms)) + (8.64e+7 * 1)) - 40089792

day_3 <- df %>% filter(date == "06.06.2021")

  day_3$ms <- (as.numeric(unlist(day_3$ms)) + (8.64e+7 * 2)) - 40089792

day_4 <- df %>% filter(date == "06.07.2021")

  day_4$ms <- (as.numeric(unlist(day_4$ms)) + (8.64e+7 * 3)) - 40089792

day_5 <- df %>% filter(date == "06.08.2021")

  day_5$ms <- (as.numeric(unlist(day_5$ms)) + (8.64e+7 * 4)) - 40089792
  
day_6 <- df %>% filter(date == "06.09.2021")

  day_6$ms <- (as.numeric(unlist(day_6$ms)) + (8.64e+7 * 5)) - 40089792

day_7 <- df %>% filter(date == "06.10.2021")

  day_7$ms <- (as.numeric(unlist(day_7$ms)) + (8.64e+7 * 6)) - 40089792

df <- rbind(day_1, day_2, day_3, day_4, day_5, day_6, day_7)

df$ms <- as.character(df$ms)

as.data.frame(df[37200:37300, ])
```
```{r}
df <- df[!is.na(df$data),]

dfx<-data.frame(data=c("900133000459724", "900133000459725",
                   "900133000459723","900133000459727",
                   "900133000459722", "900133000459721",
                   "900133000459719", "900133000459693"),
            mouse = c(4,4,3,3,2,2,1,1)
            )
 getwd()
 write.csv(dfx,"raw_data/mouseids.csv", row.names = F)

dfx <- read_csv("raw_data/mouseids.csv")
```

```{r}
mouse1 <- subset(df, data %in% dfx[dfx$mouse==1,]$data) %>% mutate(mouse = 1)
mouse2 <- subset(df, data %in% dfx[dfx$mouse==2,]$data) %>% mutate(mouse = 2)
mouse3 <- subset(df, data %in% dfx[dfx$mouse==3,]$data) %>% mutate(mouse = 3)
mouse4 <- subset(df, data %in% dfx[dfx$mouse==4,]$data) %>% mutate(mouse = 4)
```

```{r}
zz <- rbind(mouse1 %>% mutate(mouse="m1"), 
            mouse2 %>% mutate(mouse="m2"), 
            mouse3 %>% mutate(mouse="m3"), 
            mouse4 %>% mutate(mouse="m4"))
            
  li <- strsplit(zz$datetimestamp,split=":")
  hrs <- as.numeric(unlist(lapply(li, function(x) substr(x[[1]],12,13))))
  mins <- as.numeric(unlist(lapply(li, function(x) x[2])))
  secs <- as.numeric(unlist(lapply(li, function(x) x[3])))
  ms <- as.numeric(unlist(lapply(li, function(x) x[4])))

  time <- strptime(zz$datetimestamp, format="%d.%M.%Y %H:%M:%S:%OS")
  times <- strftime(time, format="%H:%M:%S:%OS")
  
  zz$times <- times
  zz$hrs <- hrs
  zz$mins <- mins
  zz$bin <- ifelse(mins>30, paste0(zz$hrs,"b"), paste0(zz$hrs, "a"))
  zz$totalmins <- (zz$hrs * 60) + zz$mins 
  
act_plot <-  ggplot(zz, aes(x=totalmins)) + 
  geom_histogram(binwidth=1,fill='lightseagreen', color='darkgreen') +
  theme_classic()+
  xlab("Time of Day in Minutes") +
 geom_vline(xintercept=c(660, 1380), color='black', lwd=1,lty=2) + 
    facet_grid(rows = vars(mouse), cols = vars(date))

# show(act_plot)
```

```{r}
tube_errors <- function(df, pair1=c(1,2), pair2=c(3,4)){
  
  ids <- c(pair1,pair2)
  codes <- c("3","19", "17", "9")
  
  x <- codes[match(df$deviceid, ids)]
  
  row.inds <-
    c(intersect(which(x == "3"), which(lag(x) == "19")),
      intersect(which(x == "19"), which(lag(x) == "3")),
      intersect(which(x == "17"),which(lag(x) == "9")),
      intersect(which(x == "9"), which(lag(x) == "17"))
      )
  
  df$error <- FALSE
  df[row.inds,"error"]<-TRUE

  
  return(df)
  }

mouse1_error <- as.data.frame(tube_errors(mouse1, pair1 = c(3,19), pair2 = c(17,9))) %>% filter(error==TRUE)
mouse2_error <- as.data.frame(tube_errors(mouse2, pair1 = c(3,19), pair2 = c(17,9))) %>% filter(error==TRUE)
mouse3_error <- as.data.frame(tube_errors(mouse3, pair1 = c(3,19), pair2 = c(17,9))) %>% filter(error==TRUE)
mouse4_error <- as.data.frame(tube_errors(mouse4, pair1 = c(3,19), pair2 = c(17,9))) %>% filter(error==TRUE)
```


```{r}
error_plot <- rbind(mouse1_error, 
                    mouse2_error, 
                    mouse3_error, 
                    mouse4_error)

li <- strsplit(error_plot$datetimestamp,split=":")
  hrs <- as.numeric(unlist(lapply(li, function(x) substr(x[[1]],12,13))))
  mins <- as.numeric(unlist(lapply(li, function(x) x[2])))
  secs <- as.numeric(unlist(lapply(li, function(x) x[3])))
  ms <- as.numeric(unlist(lapply(li, function(x) x[4])))

  time <- strptime(error_plot$datetimestamp, format="%d.%M.%Y %H:%M:%S:%OS")
  times <- strftime(time, format="%H:%M:%S:%OS")
  
  error_plot$times <- times
  error_plot$hrs <- hrs
  error_plot$mins <- mins
  error_plot$bin <- ifelse(mins>30, paste0(error_plot$hrs,"b"), paste0(error_plot$hrs, "a"))
  error_plot$totalmins <- (error_plot$hrs * 60) + error_plot$mins 
  
err_plot <- ggplot(error_plot, aes(x=totalmins)) + 
  geom_histogram(binwidth=1,fill='lightseagreen', color='darkgreen') +
  theme_classic()+
  xlab("Time of Day in Minutes") +
 geom_vline(xintercept=c(660, 1380), color='black', lwd=1,lty=2) + 
    facet_grid(rows = vars(mouse), cols = vars(date))
 
# show(err_plot)
```

```{r}
table(mouse1_error$deviceid)
table(mouse2_error$deviceid)
table(mouse3_error$deviceid)
table(mouse4_error$deviceid)

# mouse1: 20,785 rows, 130 errors
# mouse 2: 7,380 rows, 133 errors
# mouse 3: 17,121 rows, 36 errors
# mouse 4: 9,384 rows, 45 errors

##observations:
# mouse 2 has fewest entries yet most errors
# mouse 3 is active almost as much as mouse 1 but has 1/4 the errors
```


function that creates zones for each mouse and keeps the first and last of repeating zones
```{r}
zone <- function(df){
  df$row <- 1:nrow(df)
  df$deviceid <- as.numeric(df$deviceid)
  df$antennaID <- as.numeric(df$antennaID)
  
  z1 <- filter(df, deviceid==17 & antennaID==2 | deviceid==3 & antennaID==1)
  z2 <-filter(df, deviceid==3 & antennaID==2 | deviceid==9 & antennaID==1)
  z3 <-filter(df, deviceid==9 & antennaID==2 | deviceid==19 & antennaID==1)
  z4 <- filter(df, deviceid==19 & antennaID==2 | deviceid==17 & antennaID==1)
  
  z1$zone=1
  z2$zone=2
  z3$zone=3
  z4$zone=4
  
  zone_df <- rbind(z1,z2,z3,z4)
  zone_df <- arrange(zone_df, row)
  
  x <- zone_df$zone
  x1 <- sort(unique(c(length(x) - cumsum(rle(rev(x))$lengths) + 1, cumsum(rle(x)$lengths) )))
  x1 <- unlist(x1)
  
  zone_df <- zone_df[x1,]
  }

mouse1_zone <- zone(mouse1)
mouse2_zone <- zone(mouse2)
mouse3_zone <- zone(mouse3)
mouse4_zone <- zone(mouse4)
```

adding tube errors to zone dfs for each mouse
```{r}
mouse1_zone <- tube_errors(mouse1_zone, pair1 = c(3,19), pair2 = c(17,9))
mouse2_zone <- tube_errors(mouse2_zone, pair1 = c(3,19), pair2 = c(17,9))
mouse3_zone <- tube_errors(mouse3_zone, pair1 = c(3,19), pair2 = c(17,9))
mouse4_zone <- tube_errors(mouse4_zone, pair1 = c(3,19), pair2 = c(17,9))
```

figuring out time spent within zones
```{r}
## mouse1
mouse1_zone$ms <- as.numeric(mouse1_zone$ms)

mouse1_zone <- mouse1_zone[-c(1:4), ]

mouse1_zone <- mouse1_zone %>%
  mutate(zone_duration=ms-lag(ms))
 
mouse1_zone %>%
  mutate(zone_duration=ms-lag(ms)) %>%
  group_by(zone) %>%
  summarize(total=sum(!is.na(zone_duration)))

## mouse2
mouse2_zone$ms <- as.numeric(mouse2_zone$ms)

mouse2_zone <- mouse2_zone[-c(1:22), ]

mouse2_zone <- mouse2_zone %>%
  mutate(zone_duration=ms-lag(ms))
 
mouse2_zone %>%
  mutate(zone_duration=ms-lag(ms)) %>%
  group_by(zone) %>%
  summarize(total=sum(!is.na(zone_duration)))
  
## mouse3
mouse3_zone$ms <- as.numeric(mouse3_zone$ms)

mouse3_zone <- mouse3_zone[-c(1:62), ]

mouse3_zone <- mouse3_zone %>%
  mutate(zone_duration=ms-lag(ms))
 
mouse3_zone %>%
  mutate(zone_duration=ms-lag(ms)) %>%
  group_by(zone) %>%
  summarize(total=sum(!is.na(zone_duration)))

## mouse4
mouse4_zone$ms <- as.numeric(mouse4_zone$ms)

mouse4_zone <- mouse4_zone[-c(1:35), ]

mouse4_zone <- mouse4_zone %>%
  mutate(zone_duration=ms-lag(ms))
 
mouse4_zone %>%
  mutate(zone_duration=ms-lag(ms)) %>%
  group_by(zone) %>%
  summarize(total=sum(!is.na(zone_duration)))

## observation: all 4 mice spend the most time in zone 1 and the least in zone 3
```

figuring out duration of errors
```{r}
tube_errors <- function(df, pair1=c(1,2), pair2=c(3,4)){
  
  ids <- c(pair1,pair2)
  codes <- c("3","19", "17", "9")
  
  x <- codes[match(df$deviceid, ids)]
  
  row.inds <-
    c(intersect(which(x == "3"), which(lag(x) == "19")),
      intersect(which(x == "19"), which(lag(x) == "3")),
      intersect(which(x == "17"),which(lag(x) == "9")),
      intersect(which(x == "9"), which(lag(x) == "17"))
      )
  
  df$error <- FALSE
  df[row.inds,"error"]<-TRUE

  
  return(df)
  }

mouse1_zone <- tube_errors(mouse1_zone, pair1 = c(3,19), pair2 = c(17,9))
mouse2_zone <- tube_errors(mouse2_zone, pair1 = c(3,19), pair2 = c(17,9))
mouse3_zone <- tube_errors(mouse3_zone, pair1 = c(3,19), pair2 = c(17,9))
mouse4_zone <- tube_errors(mouse4_zone, pair1 = c(3,19), pair2 = c(17,9))
```


```{r}
interval3 <- function(x){
  x1 <- x[-c(1:2)]
 out <-  x1[seq(1, length(x1), 3)] - x[seq(1, length(x), 3)] 
  return(out)
}
```

mouse1
```{r}
m1_inds = which(mouse1_zone$error == "TRUE")

m1_rows <- lapply(m1_inds, function(x) (x-1):(x+1))

m1_interval3 <- mouse1_zone[unlist(m1_rows),]

m1_error_durations <- interval3(m1_interval3$ms)

## histogram of error durations for m1
hist(m1_error_durations)

## trying to separate by day
# need to apply error duration vector to every TRUE row

mouse1_zone_true <- mouse1_zone %>% filter(error==TRUE) %>%
  mutate(error_duration=m1_error_durations)
mouse1_zone_false <- mouse1_zone %>% filter(error==FALSE) %>%
  mutate(error_duration=0)

mouse1_zone <- rbind(mouse1_zone_true, mouse1_zone_false)

mouse1_zone <- arrange(mouse1_zone, ms)

table(mouse1_zone$error_duration)

pm1 <- ggplot(mouse1_zone_true, aes(x=error_duration)) +
  geom_histogram(color="darkblue", fill="darkblue", bins=100) +
  facet_wrap(~date) +
  theme_classic() +
  xlim(0, 2200000)

```

mouse2
```{r}
m2_inds = which(mouse2_zone$error == "TRUE")

m2_rows <- lapply(m2_inds, function(x) (x-1):(x+1))

m2_interval3 <- mouse2_zone[unlist(m2_rows),]

m2_error_durations <- interval3(m2_interval3$ms)

## histogram of error durations for m1
hist(m2_error_durations)

## trying to separate by day
# need to apply error duration vector to every TRUE row

mouse2_zone_true <- mouse2_zone %>% filter(error==TRUE) %>%
  mutate(error_duration=m2_error_durations)
mouse2_zone_false <- mouse2_zone %>% filter(error==FALSE) %>%
  mutate(error_duration=0)

mouse2_zone <- rbind(mouse2_zone_true, mouse2_zone_false)

mouse2_zone <- arrange(mouse2_zone, ms)

table(mouse2_zone$error_duration)

pm2 <- ggplot(mouse2_zone_true, aes(x=error_duration)) +
  geom_histogram(color="darkblue", fill="darkblue", bins=100) +
  facet_wrap(~date) +
  theme_classic() +
  xlim(0, 2200000)
```

mouse3
```{r}
m3_inds = which(mouse3_zone$error == "TRUE")

m3_rows <- lapply(m3_inds, function(x) (x-1):(x+1))

m3_interval3 <- mouse3_zone[unlist(m3_rows),]

m3_error_durations <- interval3(m3_interval3$ms)

## histogram of error durations for m1
hist(m3_error_durations)

## trying to separate by day
# need to apply error duration vector to every TRUE row

mouse3_zone_true <- mouse3_zone %>% filter(error==TRUE) %>%
  mutate(error_duration=m3_error_durations)
mouse3_zone_false <- mouse3_zone %>% filter(error==FALSE) %>%
  mutate(error_duration=0)

mouse3_zone <- rbind(mouse3_zone_true, mouse3_zone_false)

mouse3_zone <- arrange(mouse3_zone, ms)

table(mouse3_zone$error_duration)

pm3 <- ggplot(mouse3_zone_true, aes(x=error_duration)) +
  geom_histogram(color="darkblue", fill="darkblue", bins=100) +
  facet_wrap(~date) +
  theme_classic() +
  xlim(0, 2200000)
```

mouse4
```{r}
m4_inds = which(mouse4_zone$error == "TRUE")

m4_rows <- lapply(m4_inds, function(x) (x-1):(x+1))

m4_interval3 <- mouse4_zone[unlist(m4_rows),]

m4_error_durations <- interval3(m4_interval3$ms)

## histogram of error durations for m1
hist(m4_error_durations)

## trying to separate by day
# need to apply error duration vector to every TRUE row

mouse4_zone_true <- mouse4_zone %>% filter(error==TRUE) %>%
  mutate(error_duration=m4_error_durations)
mouse4_zone_false <- mouse4_zone %>% filter(error==FALSE) %>%
  mutate(error_duration=0)

mouse4_zone <- rbind(mouse4_zone_true, mouse4_zone_false)

mouse4_zone <- arrange(mouse4_zone, ms)

table(mouse4_zone$error_duration)

pm4 <- ggplot(mouse4_zone_true, aes(x=error_duration)) +
  geom_histogram(color="darkblue", fill="darkblue", bins=100) +
  facet_wrap(~date) +
  theme_classic() +
  xlim(0, 2200000)
```

```{r}
mouse_error_true <- rbind(mouse1_zone_true %>% mutate(mouse="m1"), 
            mouse2_zone_true %>% mutate(mouse="m2"), 
            mouse3_zone_true %>% mutate(mouse="m3"), 
            mouse4_zone_true %>% mutate(mouse="m4"))

dur_hist <- ggplot(mouse_error_true, aes(x=error_duration)) +
  geom_histogram(color="darkblue", fill="darkblue")  + 
  facet_grid(rows = vars(mouse), cols = vars(date)) +
  xlim(0, 2200000) 
```


