---
title: "mia rfid"
output: html_document
---
loading in packages
```{r, message=FALSE}
library(tidyverse)
```

loading in data
```{r, message=FALSE}
df <- read_csv2("raw_data/Tracking/rawdata20210610.csv")
df$data <- as.character(df$data)
```

tunnel order:
3 -> 17 -> 19 -> 9
it is impossible for a mouse to go from 3 to 19 or 17 to 9
looking for these impossible connections
```{r}
mouse2 <- df %>% 
  filter(data==900133000459722 | data==900133000459721) %>%
  as.data.frame()
z <- mouse2$deviceid
rle(z)$values
```

these connections correspond to rows 116-131, 137-151, 167-172, 180-189 
``` {r}
as.data.frame(mouse2)
```

noticed that at the first impossible connection in row 116, there is an 18 min delay since the previous entry
my thoughts: could NA values correct for these?
look at row 5211
```{r, message=FALSE}
df
```

converting 'datetimestamp' into a milliseconds column
```{r}
range(df$cantimestamp)
df$time <- df$cantimestamp - min(df$cantimestamp)
df[1:10,]

plot(df$cantimestamp, type="l")
```

why does the time keep resetting back back to 0? was filming paused?
using this subtraction method won't work for the time elapsed column 

look at row 976
```{r}
df
```

trying to figure out how to make the starting time 0 and every entry after that the time elapsed since

```{r}
library(lubridate)
x <- strptime(as.character(df$datetimestamp),'%d.%m.%Y %H:%M:%S:%OS')
time_elapsed <- x[1] %--% x[50]
time_elapsed <- as.duration(time_elapsed)
time_period <- as.period(time_elapsed)
time_period
```

need to figure this out but with milliseconds
