---
title: "mia_rfid"
output: html_document
---
### Overview and Setup
For this project, we have been using radio frequency identification data to map social hierarchies within cohorts of mice. From our setup shown below, we can use the RFID raw data to collect different pieces of information that help us put together a picture of social rank and dominance.These are some of the questions we seek to answer:
How fast are mice moving? Is one mouse being chased/is one mouse the chaser?
Where are mice spending most of their time? Are they spending time together in the same cage?
Which mouse moves the most and explores the most territory?
How active are mice throughout the day?
  
!(cage_antenna_setup.pptx)

This document is an explanation of the analysis of our RFID data.

### Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(data.table)
library(gridExtra)
```


### Raw Data
The raw data includes the following 5 columns: cantimestamp (an internal computer variable), datetimestamp (includes date and time reading), deviceid (tube), antennaid (antenna on its corresponding tube), data (the tag from the mouse that was read).

Each trial includes 2 cohorts of 6 mice each and the trial spans 11 days. There are 10 total stable cohorts used in this trial. In this chunk, I combined each set of 11 lists (days) into a dataframe to represent each pair of cohorts. I then created a mouse column by finding overlaps in the data column and a separate file containing mice ids.
```{r}
## loading in raw data from tracking behavior folder
temp <- list.files(path="data_raw/tracking_behavior/",pattern="*.csv")
xfiles <- lapply(temp, function(x) read_csv2(paste0("data_raw/tracking_behavior/",x)) )                 
lapply(xfiles, head)
lapply(xfiles, colnames)
myfiles1 <- Map(cbind, xfiles)

## separating lists by trial (11 lists per trial)
c12 <- myfiles1[c(1:11)] 
c12_df <- do.call('rbind', c12)
c12_df$cohort <- ifelse(c12_df$deviceid %in% c(1,2,3,4,8,9), 1,2 )

c34 <- myfiles1[c(12:22)] 
c34_df <-  do.call('rbind',c34)
c34_df$cohort <- ifelse(c34_df$deviceid %in% c(1,2,3,4,8,9), 3,4 )

c56 <- myfiles1[c(23:33)] 
c56_df <-  do.call('rbind',c56)
c56_df$cohort <- ifelse(c56_df$deviceid %in% c(1,2,3,4,8,9), 5,6 )

c78 <- myfiles1[c(34:45)] 
c78_df <-  do.call('rbind',c78)
c78_df$cohort <- ifelse(c78_df$deviceid %in% c(1,2,3,4,8,9), 7,8 )

c910 <- myfiles1[c(46:57)] 
c910_df <-  do.call('rbind',c910)
c910_df$cohort <- ifelse(c910_df$deviceid %in% c(1,2,3,4,8,9), 9,10 )

l <- list("c12" = c12_df , "c34" = c34_df, "c56" = c56_df, "c78" = c78_df, "c910" = c910_df)
l <- lapply(l, head)

## loading in id data 
ids <- read_csv("data_raw/id_data.csv")
id_data <- ids[,1:5]
id_data$back_tag <- as.character(id_data$back_tag)
id_data$leg_tag <- as.character(id_data$leg_tag)

id <- id_data %>%
  pivot_longer(4:5)

colnames(id) <- c("cohort", "pre_id", "mouse", "name", "data")

## creating a mouse column by combing overlapping tags in id data and tracking data
id1 <- id %>%
  filter(cohort==1)
c1_df <- c12_df %>%
  filter(cohort==1)
m1.1 <- subset(c1_df, data %in% id1[id1$mouse==1,]$data) %>% mutate(mouse = 1)
m1.3 <- subset(c1_df, data %in% id1[id1$mouse==3,]$data) %>% mutate(mouse = 3)
m1.4 <- subset(c1_df, data %in% id1[id1$mouse==4,]$data) %>% mutate(mouse = 4)
m1.6 <- subset(c1_df, data %in% id1[id1$mouse==6,]$data) %>% mutate(mouse = 6)
m1.7 <- subset(c1_df, data %in% id1[id1$mouse==7,]$data) %>% mutate(mouse = 7)
m1.8 <- subset(c1_df, data %in% id1[id1$mouse==8,]$data) %>% mutate(mouse = 8)
c1df <- rbind(m1.1, m1.3, m1.4, m1.6, m1.7, m1.8)
id2 <- id %>%
  filter(cohort==2)
c2_df <- c12_df %>%
  filter(cohort==2)
m2.1 <- subset(c2_df, data %in% id2[id2$mouse==1,]$data) %>% mutate(mouse = 1)
m2.3 <- subset(c2_df, data %in% id2[id2$mouse==3,]$data) %>% mutate(mouse = 3)
m2.4 <- subset(c2_df, data %in% id2[id2$mouse==4,]$data) %>% mutate(mouse = 4)
m2.6 <- subset(c2_df, data %in% id2[id2$mouse==6,]$data) %>% mutate(mouse = 6)
m2.7 <- subset(c2_df, data %in% id2[id2$mouse==7,]$data) %>% mutate(mouse = 7)
m2.8 <- subset(c2_df, data %in% id2[id2$mouse==8,]$data) %>% mutate(mouse = 8)
c2df <- rbind(m2.1, m2.3, m2.4, m2.6, m2.7, m2.8)
c12df <- rbind(c1df, c2df)

id3 <- id %>%
  filter(cohort==3)
c3_df <- c34_df %>%
  filter(cohort==3)
m3.2 <- subset(c3_df, data %in% id3[id3$mouse==2,]$data) %>% mutate(mouse = 2)
m3.3 <- subset(c3_df, data %in% id3[id3$mouse==3,]$data) %>% mutate(mouse = 3)
m3.4 <- subset(c3_df, data %in% id3[id3$mouse==4,]$data) %>% mutate(mouse = 4)
m3.5 <- subset(c3_df, data %in% id3[id3$mouse==5,]$data) %>% mutate(mouse = 5)
m3.6 <- subset(c3_df, data %in% id3[id3$mouse==6,]$data) %>% mutate(mouse = 6)
m3.7 <- subset(c3_df, data %in% id3[id3$mouse==7,]$data) %>% mutate(mouse = 7)
c3df <- rbind(m3.2, m3.3, m3.4, m3.5, m3.6, m3.7)
id4 <- id %>%
  filter(cohort==4)
c4_df <- c34_df %>%
  filter(cohort==4)
m4.2 <- subset(c4_df, data %in% id4[id4$mouse==2,]$data) %>% mutate(mouse = 2)
m4.3 <- subset(c4_df, data %in% id4[id4$mouse==3,]$data) %>% mutate(mouse = 3)
m4.4 <- subset(c4_df, data %in% id4[id4$mouse==4,]$data) %>% mutate(mouse = 4)
m4.5 <- subset(c4_df, data %in% id4[id4$mouse==5,]$data) %>% mutate(mouse = 5)
m4.6 <- subset(c4_df, data %in% id4[id4$mouse==6,]$data) %>% mutate(mouse = 6)
m4.7 <- subset(c4_df, data %in% id4[id4$mouse==7,]$data) %>% mutate(mouse = 7)
c4df <- rbind(m4.2, m4.3, m4.4, m4.5, m4.6, m4.7)
c34df <- rbind(c3df, c4df)

id5 <- id %>%
  filter(cohort==5)
c5_df <- c56_df %>%
  filter(cohort==5)
m5.1 <- subset(c5_df, data %in% id5[id5$mouse==1,]$data) %>% mutate(mouse = 1)
m5.4 <- subset(c5_df, data %in% id5[id5$mouse==4,]$data) %>% mutate(mouse = 4)
m5.5 <- subset(c5_df, data %in% id5[id5$mouse==5,]$data) %>% mutate(mouse = 5)
m5.6 <- subset(c5_df, data %in% id5[id5$mouse==6,]$data) %>% mutate(mouse = 6)
m5.7 <- subset(c5_df, data %in% id5[id5$mouse==7,]$data) %>% mutate(mouse = 7)
m5.8 <- subset(c5_df, data %in% id5[id5$mouse==8,]$data) %>% mutate(mouse = 8)
c5df <- rbind(m5.1, m5.4, m5.5, m5.6, m5.7, m5.8)
id6 <- id %>%
  filter(cohort==6)
c6_df <- c56_df %>%
  filter(cohort==6)
m6.1 <- subset(c6_df, data %in% id6[id6$mouse==1,]$data) %>% mutate(mouse = 1)
m6.4 <- subset(c6_df, data %in% id6[id6$mouse==4,]$data) %>% mutate(mouse = 4)
m6.5 <- subset(c6_df, data %in% id6[id6$mouse==5,]$data) %>% mutate(mouse = 5)
m6.6 <- subset(c6_df, data %in% id6[id6$mouse==6,]$data) %>% mutate(mouse = 6)
m6.7 <- subset(c6_df, data %in% id6[id6$mouse==7,]$data) %>% mutate(mouse = 7)
m6.8 <- subset(c6_df, data %in% id6[id6$mouse==8,]$data) %>% mutate(mouse = 8)
c6df <- rbind(m6.1, m6.4, m6.5, m2.6, m2.7, m2.8)
c56df <- rbind(c5df, c6df)

id7 <- id %>%
  filter(cohort==7)
c7_df <- c78_df %>%
  filter(cohort==7)
m7.1 <- subset(c7_df, data %in% id7[id7$mouse==1,]$data) %>% mutate(mouse = 1)
m7.2 <- subset(c7_df, data %in% id7[id7$mouse==2,]$data) %>% mutate(mouse = 2)
m7.3 <- subset(c7_df, data %in% id7[id7$mouse==3,]$data) %>% mutate(mouse = 3)
m7.5 <- subset(c7_df, data %in% id7[id7$mouse==5,]$data) %>% mutate(mouse = 5)
m7.6 <- subset(c7_df, data %in% id7[id7$mouse==6,]$data) %>% mutate(mouse = 6)
m7.7 <- subset(c7_df, data %in% id7[id7$mouse==7,]$data) %>% mutate(mouse = 7)
c7df <- rbind(m7.1, m7.2, m7.3, m7.5, m7.6, m7.7)
id8 <- id %>%
  filter(cohort==8)
c8_df <- c78_df %>%
  filter(cohort==8)
m8.1 <- subset(c8_df, data %in% id8[id8$mouse==1,]$data) %>% mutate(mouse = 1)
m8.2 <- subset(c8_df, data %in% id8[id8$mouse==2,]$data) %>% mutate(mouse = 2)
m8.3 <- subset(c8_df, data %in% id8[id8$mouse==3,]$data) %>% mutate(mouse = 3)
m8.5 <- subset(c8_df, data %in% id8[id8$mouse==5,]$data) %>% mutate(mouse = 5)
m8.6 <- subset(c8_df, data %in% id8[id8$mouse==6,]$data) %>% mutate(mouse = 6)
m8.7 <- subset(c8_df, data %in% id8[id8$mouse==7,]$data) %>% mutate(mouse = 7)
c8df <- rbind(m8.1, m8.2, m8.3, m8.5, m8.6, m8.7)
c78df <- rbind(c7df, c8df)

id9 <- id %>%
  filter(cohort==9)
c9_df <- c910_df %>%
  filter(cohort==9)
m9.1 <- subset(c9_df, data %in% id9[id9$mouse==1,]$data) %>% mutate(mouse = 1)
m9.2 <- subset(c9_df, data %in% id9[id9$mouse==2,]$data) %>% mutate(mouse = 2)
m9.4 <- subset(c9_df, data %in% id9[id9$mouse==4,]$data) %>% mutate(mouse = 4)
m9.5 <- subset(c9_df, data %in% id9[id9$mouse==5,]$data) %>% mutate(mouse = 5)
m9.7 <- subset(c9_df, data %in% id9[id9$mouse==7,]$data) %>% mutate(mouse = 7)
m9.8 <- subset(c9_df, data %in% id9[id9$mouse==8,]$data) %>% mutate(mouse = 8)
c9df <- rbind(m9.1, m9.2, m9.4, m9.5, m9.7, m9.8)
id10 <- id %>%
  filter(cohort==10)
c10_df <- c910_df %>%
  filter(cohort==10)
m10.1 <- subset(c10_df, data %in% id10[id10$mouse==1,]$data) %>% mutate(mouse = 1)
m10.2 <- subset(c10_df, data %in% id10[id10$mouse==2,]$data) %>% mutate(mouse = 2)
m10.4 <- subset(c10_df, data %in% id10[id10$mouse==4,]$data) %>% mutate(mouse = 4)
m10.5 <- subset(c10_df, data %in% id10[id10$mouse==5,]$data) %>% mutate(mouse = 5)
m10.7 <- subset(c10_df, data %in% id10[id10$mouse==7,]$data) %>% mutate(mouse = 7)
m10.8 <- subset(c10_df, data %in% id10[id10$mouse==8,]$data) %>% mutate(mouse = 8)
c10df <- rbind(m10.1, m10.2, m10.4, m10.5, m10.7, m10.8)
c910df <- rbind(c9df, c10df)
```


### Data and Time Format
## Creating a New Variable: Milliseconds
First, I have separated the data in datetimestamp into 2 separate columns, date and time. I then created a milliseconds column by factoring in the millisecond multiplier for hours, minutes, and seconds. Each day has to be factored in as well, because 8.64e+7 ms is added for every day that has passed. Then, the initial amount of ms is subtracted from all values to have a baseline of 0 ms.
```{r}
## creating milliseconds colum for each trial
c12df$date <- format(as.POSIXct(c12df$datetimestamp,format="%d.%m.%Y %H:%M:%S:%OS"),"%m.%d.%Y")
c12df$time <- sub("^\\S+\\s+", '', c12df$datetimestamp)
xx <- strsplit(c12df$time, split=":")
xxx <- matrix(unlist(xx), ncol = 4, byrow = TRUE)
c12df$ms<-
  (3600000 * as.numeric(xxx[,1])) +
  (60000 * as.numeric(xxx[,2])) +
  (1000 * as.numeric(xxx[,3])) +
  (1 * as.numeric(xxx[,4]))
c12df <- c12df %>%
  arrange(date)
c12_d1 <- c12df %>% filter(date == "09.27.2021")
c12_d1$ms <- as.numeric(unlist(c12_d1$ms)) 
c12_d2 <- c12df %>% filter(date == "09.28.2021")
c12_d2$ms <- (as.numeric(unlist(c12_d2$ms)) + (8.64e+7 * 1)) 
c12_d3 <- c12df %>% filter(date == "09.29.2021")
c12_d3$ms <- (as.numeric(unlist(c12_d3$ms)) + (8.64e+7 * 2)) 
c12_d4 <- c12df %>% filter(date == "09.30.2021")
c12_d4$ms <- (as.numeric(unlist(c12_d4$ms)) + (8.64e+7 * 3)) 
c12_d5 <- c12df %>% filter(date == "10.01.2021")
c12_d5$ms <- (as.numeric(unlist(c12_d5$ms)) + (8.64e+7 * 4)) 
c12_d6 <- c12df %>% filter(date == "10.02.2021")
c12_d6$ms <- (as.numeric(unlist(c12_d6$ms)) + (8.64e+7 * 5)) 
c12_d7 <- c12df %>% filter(date == "10.03.2021")
c12_d7$ms <- (as.numeric(unlist(c12_d7$ms)) + (8.64e+7 * 6)) 
c12_d8 <- c12df %>% filter(date == "10.04.2021")
c12_d8$ms <- (as.numeric(unlist(c12_d8$ms)) + (8.64e+7 * 7)) 
c12_d9 <- c12df %>% filter(date == "10.05.2021")
c12_d9$ms <- (as.numeric(unlist(c12_d9$ms)) + (8.64e+7 * 8)) 
c12_d10 <- c12df %>% filter(date == "10.06.2021")
c12_d10$ms <- (as.numeric(unlist(c12_d10$ms)) + (8.64e+7 * 9)) 
c12_d11 <- c12df %>% filter(date == "10.07.2021")
c12_d11$ms <- (as.numeric(unlist(c12_d11$ms)) + (8.64e+7 * 10)) 
c12m <- rbind(c12_d1, c12_d2, c12_d3, c12_d4, c12_d5, c12_d6, c12_d7, c12_d8, c12_d9, c12_d10, c12_d11)
c12m <- c12m %>%
  arrange(ms)
c12m$ms <- c12m$ms - 39124161
c12m$data <- as.character(c12m$data)

c34df$date <- format(as.POSIXct(c34df$datetimestamp,format="%d.%m.%Y %H:%M:%S:%OS"),"%m.%d.%Y")
c34df$time <- sub("^\\S+\\s+", '', c34df$datetimestamp)
xx <- strsplit(c34df$time, split=":")
xxx <- matrix(unlist(xx), ncol = 4, byrow = TRUE)
c34df$ms<-
  (3600000 * as.numeric(xxx[,1])) +
  (60000 * as.numeric(xxx[,2])) +
  (1000 * as.numeric(xxx[,3])) +
  (1 * as.numeric(xxx[,4]))
c34df <- c34df %>%
  arrange(date)
c34_d1 <- c34df %>% filter(date == "10.18.2021")
c34_d1$ms <- as.numeric(unlist(c34_d1$ms)) 
c34_d2 <- c34df %>% filter(date == "10.19.2021")
c34_d2$ms <- (as.numeric(unlist(c34_d2$ms)) + (8.64e+7 * 1)) 
c34_d3 <- c34df %>% filter(date == "10.20.2021")
c34_d3$ms <- (as.numeric(unlist(c34_d3$ms)) + (8.64e+7 * 2)) 
c34_d4 <- c34df %>% filter(date == "10.21.2021")
c34_d4$ms <- (as.numeric(unlist(c34_d4$ms)) + (8.64e+7 * 3)) 
c34_d5 <- c34df %>% filter(date == "10.22.2021")
c34_d5$ms <- (as.numeric(unlist(c34_d5$ms)) + (8.64e+7 * 4)) 
c34_d6 <- c34df %>% filter(date == "10.23.2021")
c34_d6$ms <- (as.numeric(unlist(c34_d6$ms)) + (8.64e+7 * 5)) 
c34_d7 <- c34df %>% filter(date == "10.24.2021")
c34_d7$ms <- (as.numeric(unlist(c34_d7$ms)) + (8.64e+7 * 6)) 
c34_d8 <- c34df %>% filter(date == "10.25.2021")
c34_d8$ms <- (as.numeric(unlist(c34_d8$ms)) + (8.64e+7 * 7)) 
c34_d9 <- c34df %>% filter(date == "10.26.2021")
c34_d9$ms <- (as.numeric(unlist(c34_d9$ms)) + (8.64e+7 * 8)) 
c34_d10 <- c34df %>% filter(date == "10.27.2021")
c34_d10$ms <- (as.numeric(unlist(c34_d10$ms)) + (8.64e+7 * 9)) 
c34_d11 <- c34df %>% filter(date == "10.28.2021")
c34_d11$ms <- (as.numeric(unlist(c34_d11$ms)) + (8.64e+7 * 10)) 
c34m <- rbind(c34_d1, c34_d2, c34_d3, c34_d4, c34_d5, c34_d6, c34_d7, c34_d8, c34_d9, c34_d10, c34_d11)
c34m <- c34m %>%
  arrange(ms)
c34m$ms <- c34m$ms - 39209615
c34m$data <- as.character(c34m$data)


c56df$date <- format(as.POSIXct(c56df$datetimestamp,format="%d.%m.%Y %H:%M:%S:%OS"),"%m.%d.%Y")
c56df$time <- sub("^\\S+\\s+", '', c56df$datetimestamp)
xx <- strsplit(c56df$time, split=":")
xxx <- matrix(unlist(xx), ncol = 4, byrow = TRUE)
c56df$ms<-
  (3600000 * as.numeric(xxx[,1])) +
  (60000 * as.numeric(xxx[,2])) +
  (1000 * as.numeric(xxx[,3])) +
  (1 * as.numeric(xxx[,4]))
c56df <- c56df %>%
  arrange(date)
c56df <- c56df %>%
  filter(cohort==5 | cohort ==6)
c56_d1 <- c56df %>% filter(date == "11.08.2021")
c56_d1$ms <- as.numeric(unlist(c56_d1$ms)) 
c56_d2 <- c56df %>% filter(date == "11.09.2021")
c56_d2$ms <- (as.numeric(unlist(c56_d2$ms)) + (8.64e+7 * 1)) 
c56_d3 <- c56df %>% filter(date == "11.10.2021")
c56_d3$ms <- (as.numeric(unlist(c56_d3$ms)) + (8.64e+7 * 2)) 
c56_d4 <- c56df %>% filter(date == "11.11.2021")
c56_d4$ms <- (as.numeric(unlist(c56_d4$ms)) + (8.64e+7 * 3)) 
c56_d5 <- c56df %>% filter(date == "11.12.2021")
c56_d5$ms <- (as.numeric(unlist(c56_d5$ms)) + (8.64e+7 * 4)) 
c56_d6 <- c56df %>% filter(date == "11.13.2021")
c56_d6$ms <- (as.numeric(unlist(c56_d6$ms)) + (8.64e+7 * 5)) 
c56_d7 <- c56df %>% filter(date == "11.14.2021")
c56_d7$ms <- (as.numeric(unlist(c56_d7$ms)) + (8.64e+7 * 6)) 
c56_d8 <- c56df %>% filter(date == "11.15.2021")
c56_d8$ms <- (as.numeric(unlist(c56_d8$ms)) + (8.64e+7 * 7)) 
c56_d9 <- c56df %>% filter(date == "11.16.2021")
c56_d9$ms <- (as.numeric(unlist(c56_d9$ms)) + (8.64e+7 * 8)) 
c56_d10 <- c56df %>% filter(date == "11.17.2021")
c56_d10$ms <- (as.numeric(unlist(c56_d10$ms)) + (8.64e+7 * 9)) 
c56_d11 <- c56df %>% filter(date == "11.18.2021")
c56_d11$ms <- (as.numeric(unlist(c56_d11$ms)) + (8.64e+7 * 10))
c56m <- rbind(c56_d1, c56_d2, c56_d3, c56_d4, c56_d5, c56_d6, c56_d7, c56_d8, c56_d9, c56_d10, c56_d11)
c56m <- c56m %>%
  arrange(ms)
c56m$ms <- c56m$ms - 35017088
c56m$data <- as.character(c56m$data)

c78df$date <- format(as.POSIXct(c78df$datetimestamp,format="%d.%m.%Y %H:%M:%S:%OS"),"%m.%d.%Y")
c78df$time <- sub("^\\S+\\s+", '', c78df$datetimestamp)
xx <- strsplit(c78df$time, split=":")
xxx <- matrix(unlist(xx), ncol = 4, byrow = TRUE)
c78df$ms <-
  (3600000 * as.numeric(xxx[,1])) +
  (60000 * as.numeric(xxx[,2])) +
  (1000 * as.numeric(xxx[,3])) +
  (1 * as.numeric(xxx[,4]))
c78df <- c78df %>%
  arrange(date)
c78df <- c78df %>%
  filter(cohort==7 | cohort ==8)
c78_d1 <- c78df %>% filter(date == "11.22.2021")
c78_d1$ms <- as.numeric(unlist(c78_d1$ms)) 
c78_d2 <- c78df %>% filter(date == "11.23.2021")
c78_d2$ms <- (as.numeric(unlist(c78_d2$ms)) + (8.64e+7 * 1)) 
c78_d3 <- c78df %>% filter(date == "11.24.2021")
c78_d3$ms <- (as.numeric(unlist(c78_d3$ms)) + (8.64e+7 * 2)) 
c78_d4 <- c78df %>% filter(date == "11.25.2021")
c78_d4$ms <- (as.numeric(unlist(c78_d4$ms)) + (8.64e+7 * 3)) 
c78_d5 <- c78df %>% filter(date == "11.26.2021")
c78_d5$ms <- (as.numeric(unlist(c78_d5$ms)) + (8.64e+7 * 4)) 
c78_d6 <- c78df %>% filter(date == "11.27.2021")
c78_d6$ms <- (as.numeric(unlist(c78_d6$ms)) + (8.64e+7 * 5)) 
c78_d7 <- c78df %>% filter(date == "11.28.2021")
c78_d7$ms <- (as.numeric(unlist(c78_d7$ms)) + (8.64e+7 * 6)) 
c78_d8 <- c78df %>% filter(date == "11.29.2021")
c78_d8$ms <- (as.numeric(unlist(c78_d8$ms)) + (8.64e+7 * 7)) 
c78_d9 <- c78df %>% filter(date == "11.30.2021")
c78_d9$ms <- (as.numeric(unlist(c78_d9$ms)) + (8.64e+7 * 8)) 
c78_d10 <- c78df %>% filter(date == "12.01.2021")
c78_d10$ms <- (as.numeric(unlist(c78_d10$ms)) + (8.64e+7 * 9)) 
c78_d11 <- c78df %>% filter(date == "12.02.2021")
c78_d11$ms <- (as.numeric(unlist(c78_d11$ms)) + (8.64e+7 * 10))
c78m <- rbind(c78_d1, c78_d2, c78_d3, c78_d4, c78_d5, c78_d6, c78_d7, c78_d8, c78_d9, c78_d10, c78_d11)
c78m <- c78m %>%
  arrange(ms)
c78m$ms <- c78m$ms - 35136408
c78m$data <- as.character(c78m$data)


c910df$date <- format(as.POSIXct(c910df$datetimestamp,format="%d.%m.%Y %H:%M:%S:%OS"),"%m.%d.%Y")
c910df$time <- sub("^\\S+\\s+", '', c910df$datetimestamp)
xx <- strsplit(c910df$time, split=":")
xxx <- matrix(unlist(xx), ncol = 4, byrow = TRUE)
c910df$ms<-
  (3600000 * as.numeric(xxx[,1])) +
  (60000 * as.numeric(xxx[,2])) +
  (1000 * as.numeric(xxx[,3])) +
  (1 * as.numeric(xxx[,4]))
c910df <- c910df %>%
  arrange(date)
c910df <- c910df %>%
  filter(cohort==9 | cohort ==10)
c910_d1 <- c910df %>% filter(date == "01.17.2022")
c910_d1$ms <- as.numeric(unlist(c910_d1$ms)) 
c910_d2 <- c910df %>% filter(date == "01.18.2022")
c910_d2$ms <- (as.numeric(unlist(c910_d2$ms)) + (8.64e+7 * 1)) 
c910_d3 <- c910df %>% filter(date == "01.19.2022")
c910_d3$ms <- (as.numeric(unlist(c910_d3$ms)) + (8.64e+7 * 2)) 
c910_d4 <- c910df %>% filter(date == "01.20.2022")
c910_d4$ms <- (as.numeric(unlist(c910_d4$ms)) + (8.64e+7 * 3)) 
c910_d5 <- c910df %>% filter(date == "01.21.2022")
c910_d5$ms <- (as.numeric(unlist(c910_d5$ms)) + (8.64e+7 * 4)) 
c910_d6 <- c910df %>% filter(date == "01.22.2022")
c910_d6$ms <- (as.numeric(unlist(c910_d6$ms)) + (8.64e+7 * 5)) 
c910_d7 <- c910df %>% filter(date == "01.23.2022")
c910_d7$ms <- (as.numeric(unlist(c910_d7$ms)) + (8.64e+7 * 6)) 
c910_d8 <- c910df %>% filter(date == "01.24.2022")
c910_d8$ms <- (as.numeric(unlist(c910_d8$ms)) + (8.64e+7 * 7)) 
c910_d9 <- c910df %>% filter(date == "01.25.2022")
c910_d9$ms <- (as.numeric(unlist(c910_d9$ms)) + (8.64e+7 * 8)) 
c910_d10 <- c910df %>% filter(date == "01.26.2022")
c910_d10$ms <- (as.numeric(unlist(c910_d10$ms)) + (8.64e+7 * 9)) 
c910_d11 <- c910df %>% filter(date == "01.27.2022")
c910_d11$ms <- (as.numeric(unlist(c910_d11$ms)) + (8.64e+7 * 10))
c910m <- rbind(c910_d1, c910_d2, c910_d3, c910_d4, c910_d5, c910_d6, c910_d7, c910_d8, c910_d9, c910_d10, c910_d11)
c910m <- c910m %>%
  arrange(ms)
c910m$ms <- c910m$ms - 86379953
c910m$data <- as.character(c910m$data)
```


### Activity Plots
In this code, we've created a function to map activity split by mouse and date. These plots are histograms, where a reading in the raw data is equal to 1.
```{r}
## creating an activity plot function
activity.plot <- function(act){

li <- strsplit(act$datetimestamp,split=":")
hrs <- as.numeric(unlist(lapply(li, function(x) substr(x[[1]],12,13))))
mins <- as.numeric(unlist(lapply(li, function(x) x[2])))
secs <- as.numeric(unlist(lapply(li, function(x) x[3])))
ms <- as.numeric(unlist(lapply(li, function(x) x[4])))

time <- strptime(act$datetimestamp, format="%d.%M.%Y %H:%M:%S:%OS")
times <- strftime(time, format="%H:%M:%S:%OS")

act$times <- times
act$hrs <- hrs
act$mins <- mins
act$bin <- ifelse(mins>30, paste0(act$hrs,"b"), paste0(act$hrs, "a"))
act$totalmins <- (act$hrs * 60) + act$mins 

act_plot <-  ggplot(act, aes(x=totalmins)) + 
  geom_histogram(binwidth=1,fill='lightseagreen', color='darkgreen') +
  theme_classic()+
  xlab("Time of Day in Minutes") +
  geom_vline(xintercept=c(660, 1380), color='black', lwd=1,lty=2) + 
  facet_grid(rows = vars(mouse), cols = vars(date)) +
  ggtitle("activity plot")

show(act_plot)
}

c1.act <- c12m %>%
  filter(cohort==1)
c2.act <- c12m %>%
  filter(cohort==2)
c3.act <- c34m %>%
  filter(cohort==3)
c4.act <- c34m %>%
  filter(cohort==4)
c5.act <- c56m %>%
  filter(cohort==5)
c6.act <- c56m %>%
  filter(cohort==6)
c7.act <- c78m %>%
  filter(cohort==7)
c8.act <- c78m %>%
  filter(cohort==8)
c9.act <- c910m %>%
  filter(cohort==9)
c10.act <- c910m %>%
  filter(cohort==10)

c1.act <- activity.plot(as.data.frame(c1.act))
c2.act <- activity.plot(as.data.frame(c2.act))
c3.act <- activity.plot(as.data.frame(c3.act))
c4.act <- activity.plot(as.data.frame(c4.act))
c5.act <- activity.plot(as.data.frame(c5.act))
c6.act <- activity.plot(as.data.frame(c6.act))
c7.act <- activity.plot(as.data.frame(c7.act))
c8.act <- activity.plot(as.data.frame(c8.act))
c9.act <- activity.plot(as.data.frame(c9.act))
c10.act <- activity.plot(as.data.frame(c10.act))
```

### Errors


### Zones
The following functions break up the set ups into different "zones". Zones are made by enclosing each cage by antenna. Each zone includes at least one antenna in order to section off cages appropriately.
```{r}
# zone function for cohorts 1, 3, 5, 7, 9
zone.1 <- function(df){
  df$row <- 1:nrow(df)
  df$deviceid <- as.numeric(df$deviceid)
  df$antennaID <- as.numeric(df$antennaID)
  
  z1 <- filter(df, deviceid==1 & antennaID==1)
  z2 <- filter(df, deviceid==1 & antennaID==2 | deviceid==2 & antennaID==1)
  z3 <- filter(df, deviceid==2 & antennaID==2 | deviceid==3 & antennaID==1 | deviceid==8 & antennaID==1)
  z4 <- filter(df, deviceid==3 & antennaID==2 | deviceid==4 & antennaID==1)
  z5 <- filter(df, deviceid==4 & antennaID==2 | deviceid==9 & antennaID==2)
  z6 <- filter(df, deviceid==9 & antennaID==1 | deviceid==8 & antennaID==2)
  
  z1$zone=1
  z2$zone=2
  z3$zone=3
  z4$zone=4
  z5$zone=5
  z6$zone=6
  
  zone_df <- rbind(z1,z2,z3,z4,z5,z6)
  zone_df <- arrange(zone_df, row)
  
  x <- zone_df$zone
  x1 <- sort(unique(c(length(x) - cumsum(rle(rev(x))$lengths) + 1, cumsum(rle(x)$lengths) )))
  x1 <- unlist(x1)
  
  zone_df <- zone_df[x1,]
  }

c1.act <- zone.1(c1.act)
c3.act <- zone.1(c3.act)
c5.act <- zone.1(c5.act)
c7.act <- zone.1(c7.act)
c9.act <- zone.1(c9.act)

table(c1.act$zone)
table(c3.act$zone)
table(c5.act$zone)
table(c7.act$zone)
table(c9.act$zone)

# zone function for cohorts 2, 4, 6, 8, 10
zone.2 <- function(df){
  df$row <- 1:nrow(df)
  df$deviceid <- as.numeric(df$deviceid)
  df$antennaID <- as.numeric(df$antennaID)
  
  z1 <- filter(df, deviceid==19 & antennaID==1)
  z2 <- filter(df, deviceid==19 & antennaID==2 | deviceid==18 & antennaID==1)
  z3 <- filter(df, deviceid==18 & antennaID==2 | deviceid==17 & antennaID==1 | deviceid==21 & antennaID==2)
  z4 <- filter(df, deviceid==17 & antennaID==2 | deviceid==16 & antennaID==1)
  z5 <- filter(df, deviceid==16 & antennaID==2 | deviceid==20 & antennaID==1)
  z6 <- filter(df, deviceid==20 & antennaID==2 | deviceid==21 & antennaID==1)
  
  z1$zone=1
  z2$zone=2
  z3$zone=3
  z4$zone=4
  z5$zone=5
  z6$zone=6
  
  zone_df <- rbind(z1,z2,z3,z4,z5,z6)
  zone_df <- arrange(zone_df, row)
  
  x <- zone_df$zone
  x1 <- sort(unique(c(length(x) - cumsum(rle(rev(x))$lengths) + 1, cumsum(rle(x)$lengths) )))
  x1 <- unlist(x1)
  
  zone_df <- zone_df[x1,]
  }

c2.act <- zone.2(c2.act)
c4.act <- zone.2(c4.act)
c6.act <- zone.2(c6.act)
c8.act <- zone.2(c8.act)
c10.act <- zone.2(c10.act)

table(c2.act$zone)
table(c4.act$zone)
table(c6.act$zone)
table(c8.act$zone)
table(c10.act$zone)
```


### Time spent in zones
```{r}
# food cage is cage 1

# cohort 1 
c1m1 <- c1.act %>%
  filter(mouse==1)
c1m3 <- c1.act %>%
  filter(mouse==3)
c1m4 <- c1.act %>%
  filter(mouse==4)
c1m6 <- c1.act %>%
  filter(mouse==6)
c1m7 <- c1.act %>%
  filter(mouse==7)
c1m8 <- c1.act %>%
  filter(mouse==8)

c1m1z <- c1m1 %>%
  mutate(zd=ms-lag(ms))
c1m1z %>%
  mutate(zd=ms-lag(ms)) %>%
  group_by(zone) %>%
  summarize(total=sum(!is.na(zd)))

## c1m1 spends the most amount of time in zone 3
```


### Association Plots
```{r}
# overlap, together, apart, plot functions
get_overlaps <- function(df, id1=1, id2=2){
  DT = data.table(df)
  setkey(DT, start, end)
  oDT0 = foverlaps(DT[id==id1], DT[id==id2])
  oDT0[, `:=`(
    ostart = pmax(start, i.start),
    oend = pmin(end, i.end)
  )]
  oDT = oDT0[ostart < oend]
  return(oDT)
}

# together
together <- function(df){
  oDT <- get_overlaps(df)
  oDT[zone == i.zone, .(ids = '1-2', zone, ostart, oend)]
}

# apart
apart <- function(df){
  oDT <- get_overlaps(df)
  oDTapt <- oDT[zone != i.zone, .(id, zone, i.id, i.zone, ostart, oend)]
  return(rbindlist(list(oDTapt[,c(1,2,5,6)],oDTapt[,3:6])))
}

# plot
overlap.plot <- function(df){
  p <- ggplot() + 
    geom_segment(data=df.ap, aes(x=ostart, xend=oend, y=zone, yend=zone, color=factor(id)), size=15) +
    geom_segment(data=df.to, aes(x=ostart, xend=oend, y=zone, yend=zone), color = "#571e16", size=15) +
    theme_classic() +
    scale_color_manual(values=c("#f2b03d", "#4287f5")) +
    labs(color= "mouse") +
    xlab("time since start (ms)") +
    scale_x_continuous(labels = function(x) format(x, scientific = FALSE))
  
  return(p)
}

# creating a df with start and end times for cohort 1 mice
c1m1a <- c1m1 %>% filter(date == "09.27.2021" & ms > 0 & ms < 3600000)
c1m1ap <- data.frame(
  start = c1m1a$ms,
  id = c1m1a$mouse,
  zone = c1m1a$zone)
c1m1ap$end <- lead(c1m1ap$start)
c1m1ap$end[727]<- 3535365

c1m3a <- c1m3 %>% filter(date == "09.27.2021" & ms > 0 & ms < 3600000)
c1m3ap <- data.frame(
  start = c1m3a$ms,
  id = c1m3a$mouse,
  zone = c1m3a$zone)
c1m3ap$end <- lead(c1m3ap$start)
c1m3ap$end[1032]<- 3593788

c1m4a <- c1m4 %>% filter(date == "09.27.2021" & ms > 0 & ms < 3600000)
c1m4ap <- data.frame(
  start = c1m4a$ms,
  id = c1m4a$mouse,
  zone = c1m4a$zone)
c1m4ap$end <- lead(c1m4ap$start)
c1m4ap$end[728]<- 3599236

c1m6a <- c1m6 %>% filter(date == "09.27.2021" & ms > 0 & ms < 3600000)
c1m6ap <- data.frame(
  start = c1m6a$ms,
  id = c1m6a$mouse,
  zone = c1m6a$zone)
c1m6ap$end <- lead(c1m6ap$start)
c1m6ap$end[966]<- 3598763

c1m7a <- c1m7 %>% filter(date == "09.27.2021" & ms > 0 & ms < 3600000)
c1m7ap <- data.frame(
  start = c1m7a$ms,
  id = c1m7a$mouse,
  zone = c1m7a$zone)
c1m7ap$end <- lead(c1m7ap$start)
c1m7ap$end[574]<- 3591667

c1m8a <- c1m8 %>% filter(date == "09.27.2021" & ms > 0 & ms < 3600000)
c1m8ap <- data.frame(
  start = c1m8a$ms,
  id = c1m8a$mouse,
  zone = c1m8a$zone)
c1m8ap$end <- lead(c1m8ap$start)
c1m8ap$end[460]<- 3536898

# create pairs
```


```{r}
c4.3mice <- c4.act %>%
  filter(mouse==7 | mouse==3 | mouse==2)

c4.7act <- c4.3mice %>%
  filter(mouse == 7) %>%
  mutate(rank1 = "dom")
c4.3act <- c4.3mice %>%
  filter(mouse == 3) %>%
  mutate(rank1 = "subdom")
c4.2act <- c4.3mice %>%
  filter(mouse == 2) %>%
  mutate(rank1 = "sub")

c4.7act <- c4.7act %>% filter(date == "10.19.2021")
c4.7act <- data.frame(
  start = c4.7act$ms,
  id = c4.7act$rank1,
  zone = c4.7act$zone)
c4.7act$end <- lead(c4.7act$start)
c4.7act$end[10276]<- 133563723

c4.3act <- c4.3act %>% filter(date == "10.19.2021")
c4.3act <- data.frame(
  start = c4.3act$ms,
  id = c4.3act$rank1,
  zone = c4.3act$zone)
c4.3act$end <- lead(c4.3act$start)
c4.3act$end[4429]<- 133574259

c4.2act <- c4.2act %>% filter(date == "10.19.2021")
c4.2act <- data.frame(
  start = c4.2act$ms,
  id = c4.2act$rank1,
  zone = c4.2act$zone)
c4.2act$end <- lead(c4.2act$start)
c4.2act$end[3571]<- 133509064

get_overlaps <- function(df, id1=1, id2=2){
  DT = data.table(df)
  setkey(DT, start, end)
  oDT0 = foverlaps(DT[id==id1], DT[id==id2])
  oDT0[, `:=`(
    ostart = pmax(start, i.start),
    oend = pmin(end, i.end)
  )]
  oDT = oDT0[ostart < oend]
  return(oDT)
}

c4.7act
c4.3act
c4.2act

togetherX <- function(df, ida="1", idb="2"){
  oDT <- get_overlaps(df, id1=ida, id2=idb)
  oDT[zone == i.zone, .(ids = paste0(ida,"-",idb), zone, ostart, oend)]
}

apartX <- function(df, ida="1", idb="2"){
  oDT <- get_overlaps(df, id1=ida, id2=idb)
  oDTapt <- oDT[zone != i.zone, .(id, zone, i.id, i.zone, ostart, oend)]
  return(rbindlist(list(oDTapt[,c(1,2,5,6)],oDTapt[,3:6])))
}


zone_overlap <- function(df1, df2, ida="1", idb="2"){
  
m_plot <- rbind(df1, df2)
m_plot$start <- as.numeric(m_plot$start)
m_plot$end <- as.numeric(m_plot$end)

df.ap <- apartX(m_plot, ida, idb)
df.to <- togetherX(m_plot, ida, idb)

p <- ggplot() + 
  geom_segment(data=df.ap, aes(x=ostart, xend=oend, y=zone, yend=zone, color=factor(id)), size=15) +
  geom_segment(data=df.to, aes(x=ostart, xend=oend, y=zone, yend=zone), color = "#571e16", size=15) +
  theme_classic() +
  scale_color_manual(values=c("#f2b03d", "#4287f5")) +
  labs(color= "mouse") +
  xlab("time since start (ms)") +
  scale_x_continuous(labels = function(x) format(x, scientific = FALSE))

return(p)
}

p1 <- zone_overlap(c4.7act, c4.2act, ida="dom", idb="sub") +
  scale_color_manual(values=c("#f2b03d", "#4287f5")) +
  scale_y_continuous(breaks=seq(1,10,by=1))
p2 <- zone_overlap(c4.7act, c4.3act, ida="dom", idb="subdom") +
  scale_color_manual(values=c("#f2b03d", "#FE0004")) +
  scale_y_continuous(breaks=seq(1,10,by=1))

library(gridExtra)

grid.arrange(p1, p2)
```


### In progress: Chase
